---
title: "echogithub: Getting started" 
author: "<h4>Author: <i>Brian M. Schilder</i></h4>" 
date: "<h4>Most recent update: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{echogithub} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r setup}
library(echogithub)
```

# GitHub branches

## List

Easily find all available branches for a given GitHub repo.

```{r}
branches <- echogithub::github_branches(owner = "RajLabMSSM",
                                        repo = "echolocatoR")
print(branches)
```

## Check

You can also check whether a particular branch exists.
By default, `github_branches()` interprets "master" and "main" as synonymous and 
returns whichever one actually exists.

```{r}
branches <- echogithub::github_branches(owner = "RajLabMSSM", 
                                        repo = "echolocatoR", 
                                        branch = "main")
print(branches)
```


#  GitHub files 

`github_files()` lets you easily:
1. Search any GitHub repo
(that you have access to) for files. 
2. Filter those files by a *regex* `query`,
3. Download those files to your local compute 
(can increase `nThread` to speed up download via parallelization).

*NOTE*: 
To search your private repos, make sure you
GitHub token is supplied to the `token` argument, or is saved as in your
*~.Renviron* file, e.g.: `GITHUB_TOKEN=<token_here>`

## Search / filter / downlaod

```{r}
files <- echogithub::github_files(owner = "RajLabMSSM", 
                                  repo = "Fine_Mapping_Shiny",
                                  query = ".md$",
                                  ignore.case = TRUE,
                                  download = TRUE)
knitr::kable(utils::head(files))
```

# GitHub Pages

There are several functions to searching GitHub Pages websites associated
with specific GitHub repos.

## Find GitHub Pages URL


First, since not all GitHub repo have use GitHub Pages, we should find out 
whether the one we're interested in exist. 

```{r}
ghpages_url <- echogithub::github_pages(owner ="RajLabMSSM",
                                        repo = "echolocatoR")
print(ghpages_url)
```

If it doesn't exist, the function will simply return `NULL` when you set 
`error=FALSE`.

```{r}
ghpages_null <- echogithub::github_pages(owner ="RajLabMSSM",
                                        repo = "Fine_Mapping_Shiny",
                                        error = FALSE)
print(ghpages_null)
```


## Find vignettes

`github_pages_vignettes` allows you to easily gather all vignettes 
across multiple GitHub Pages websites at once.

### As `data.table`

```{r}  
vdt <- echogithub::github_pages_vignettes(owner = c("RajLabMSSM","neurogenomics"), 
                                          repo = c("echodata","MungeSumstats"))
knitr::kable(utils::head(vdt))
```

### As table of contents

You can also use the `as_toc=TRUE` argument to turn the vignettes `data.table`
into an HTML Table of Contents (TOC).

```{r, results='asis'}
toc <-  echogithub::github_pages_vignettes(owner = c("RajLabMSSM","neurogenomics"), 
                                           repo = c("echodata","MungeSumstats"),
                                           as_toc = TRUE)
```

# *DESCRIPTION* files

*DESCRIPTION* files contains essential information about each R package.
However finding and importing them is not always straightforward 
(e.g. when the package is not yet installed).
`echogithub::description_extract` searches a variety of sources 
(e.g. local files, local installations, GitHub) to find the correct 
*DESCRIPTION* file and import it into the easy-to-use `description` format.

It then parses it to extract the relevant information.
 
## Find and extract

`description_extract` then takes that object and extracts and parses
just the fields you need, returning them as a named list.

```{r}
res <- echogithub::description_extract(refs = c("RajLabMSSM/echolocatoR",
                                                "RajLabMSSM/echogithub",
                                                "RajLabMSSM/rworkflows"))
methods::show(res)
```


# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

<hr>

